---
title: "High-level Analysis of Cohort"
author: "Patrick Kimes"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

# Outline

Here we try out doing an analysis.

```{r}
library(tidyverse)
library(lubridate)
library(cowplot)
library(bigrquery)
library(ggbeeswarm)

theme_set(theme_minimal())
theme_x_rotate <- function(...) {
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1), ...)
}

## bigrquery issue: https://github.com/r-dbi/bigrquery/issues/395
options(scipen = 20)
```

We will be querying from the same project and dataset on BigQuery.

```{r}
project <- "hst-953-2019"
bq_auth(email = "patrick.kimes@gmail.com")
```

Data tables will be saved to a local directory for easier future access.

```{r}
bqdir <- file.path("..", "data", "bigquery")
dir.create(bqdir, showWarnings = FALSE, recursive = TRUE)
```

# Data

## Cohort

First, we will download our cohort table.

```{r, eval = FALSE}
cohort_rds <- file.path(bqdir, "cohort.rds")
if (file.exists(cohort_rds)) {
    cohort <- readRDS(cohort_rds)
} else {
    bq_tab_cohort <- "hst-953-2019.bias2020.notes_by_weight"
    cohort <- bq_table_download(bq_tab_cohort, page_size = 1e3)
    saveRDS(cohort, file = cohort_rds)
}
cohort <- cohort %>%
    dplyr::distinct(HADM_ID, SUBJECT_ID, GENDER, DOB,
                    WEIGHT_MAX, HEIGHT_MAX, AGE)
```

We don't care about notes, so we'll flatten this table and also obtain the
length of stay for each admission.

```{r}
cohortmeta_rds <- file.path(bqdir, "cohortmeta.rds")
if (file.exists(cohortmeta_rds)) {
    cohortmeta <- readRDS(cohortmeta_rds)
} else {
    query <- paste("SELECT * ",
                   "FROM (",
                   "  SELECT DISTINCT HADM_ID, SUBJECT_ID, GENDER, AGE, WEIGHT_MAX, HEIGHT_MAX",
                   "  FROM `hst-953-2019.bias2020.notes_by_weight`",
                   ")",
                   "LEFT JOIN (",
                   "  SELECT HADM_ID, SUBJECT_ID, ADMITTIME, DISCHTIME, HOSPITAL_EXPIRE_FLAG",
                   "  FROM `physionet-data.mimiciii_clinical.admissions`",
                   ")",
                   "USING (HADM_ID, SUBJECT_ID)")
    cm <- bq_project_query(x = "hst-953-2019", query = query)
    cohortmeta <- bq_table_download(cm)
    saveRDS(cohortmeta, cohortmeta_rds)
}
```

Determine the length of stay for each admission.

```{r}
cohortmeta <- cohortmeta %>%
    dplyr::mutate(LOS = lubridate::time_length(DISCHTIME - ADMITTIME,
                                               unit = "days")) %>%
    dplyr::select(-ADMITTIME, -DISCHTIME)
```

We filter this cohort to only patients over 18.

```{r}
cohortmeta <- cohortmeta %>%
    dplyr::filter(AGE > 18)
```

Check for negative lengths of stay.

```{r}
cohortmeta %>%
    dplyr::arrange(LOS) %>% 
    dplyr::select(-HEIGHT_MAX) %>%
    print(n = 20)
```

A lot of these short visits are patients who died during the stay. 

```{r, fig.width = 6, fig.heigth = 3}
gp <- cohortmeta %>%
    dplyr::mutate(HOSPITAL_EXPIRE_FLAG =
                      dplyr::recode(HOSPITAL_EXPIRE_FLAG, "1" = "Yes (1)", "0" = "No (0)")) %>%
    ggplot(aes(x = HOSPITAL_EXPIRE_FLAG, y = LOS)) +
    geom_quasirandom(varwidth = TRUE, alpha = 1/2, size = 1) +
    ylab("Length of stay (days)")
gp + coord_flip()

gp + coord_flip(ylim = c(-5, 20))
```

All patients with negative lengths of stay expired in the hospital. We will exclude these patients.

```{r}
cohortmeta <- cohortmeta %>%
    dplyr::filter(LOS > 0)
```

## Turning

The following query is used to identify all potential turning events item IDs.

```{r, eval = FALSE}
## query <- paste("SELECT DISTINCT d.itemid, d.label, d.category, c.value, d.dbsource",
##                "FROM `physionet-data.mimiciii_clinical.d_items` d",
##                "LEFT JOIN `physionet-data.mimiciii_clinical.chartevents` c",
##                "ON d.itemid = c.itemid",
##                "WHERE", 
##                'lower(d.label) like "position%"',
##                'OR lower(d.label) like "patient position%"',
##                'OR lower(d.label) like "turn%"',
##                'OR lower(d.label) like "activity"',
##                'OR lower(d.label) like "assistance device"',
##                'OR lower(d.label) like "other (activity)%"',
##                'OR lower(c.value) like "%turn%"',
##                'OR lower(c.value) like "%supine%"',
##                'OR lower(c.value) like "%prone%"',
##                'OR lower(c.value) like "%cradle%"',
##                'OR lower(c.value) like "%stand"',
##                'OR lower(c.value) like "%side to side%"',
##                'OR lower(c.value) like "left side"',
##                'OR lower(c.value) like "right side"',
##                'OR lower(c.value) like "bedrest"')
## tb <- bq_project_query(x = "hst-953-2019", query = query)
## labs <- bq_table_download(tb)
```

A manually curated set of this list is available from Ken.

```{r}
labs <- read_csv(file.path("..", "data", "bigquery-annotated",
                           "patient_itemids_positive_turning_maneuver_1107.csv"),
                 col_types = cols())
labs <- dplyr::filter(labs, positive_turning_maneuver == 1)
labs <- dplyr::select(labs, -positive_turning_maneuver)
```

Query in `charevents` table.

```{r}
turnevents_rds <- file.path(bqdir, "turnevents.rds")
if (file.exists(turnevents_rds)) {
    turnevents <- readRDS(turnevents_rds)
} else {
    query <- paste("SELECT * ",
                   "FROM `physionet-data.mimiciii_clinical.chartevents` ",
                   "INNER JOIN (",
                   "  SELECT *",
                   "  FROM `hst-953-2019.bias2020.turning_itemids`",
                   "  WHERE positive_turning_maneuver = 1",
                   ") ",
                   "USING (itemid, value)")
    te <- bq_project_query(x = "hst-953-2019", query = query)
    turnevents <- bq_table_download(te)
    saveRDS(turnevents, turnevents_rds)
}
```

Flatten event counts to unique hospital admission IDs (`HADM_ID`s) since this
is how we will analyze notes.

```{r}
turncounts <- turnevents %>%
    dplyr::count(SUBJECT_ID, HADM_ID,
                 ITEMID = itemid, VALUE = value, LABEL = label)
```

Combine cohort metadata and turning event counts. 

```{r}
cohortturns <- cohortmeta %>%
    dplyr::left_join(turncounts, by = c("SUBJECT_ID", "HADM_ID"))
```

Fill in all zeros.

```{r}
cohortturns <- cohortturns %>%
    tidyr::complete(tidyr::nesting(HADM_ID, SUBJECT_ID, GENDER, AGE,
                                   WEIGHT_MAX, HEIGHT_MAX,
                                   HOSPITAL_EXPIRE_FLAG, LOS),
                    tidyr::nesting(ITEMID, VALUE, LABEL),
                    fill = list(n = 0L)) %>%
    dplyr::filter(!is.na(ITEMID))
```


# First Order

First, just do some simple counting.

```{r, fig.width = 6.5, fig.height = 3}
## check number of admissions
cohortmeta %>%
    dplyr::count(SUBJECT_ID) %>%
    ggplot(aes(x = n)) +
    geom_bar(color = 'black', fill = 'gray') +
    scale_x_continuous("number of admissions", breaks = 1:100) +
    ylab("number of subjects") +
    ggtitle("Distribution of hospital admissions by subjects")

## check number of admissions
cohortmeta %>%
    dplyr::count(SUBJECT_ID, GENDER) %>%
    ggplot(aes(x = n, fill = GENDER)) +
    geom_bar(color = 'black', position = 'dodge') +
    scale_x_continuous("number of admissions", breaks = 1:100) +
    ylab("number of subjects") +
    ggtitle("Distribution of hospital admissions by subjects")

## check distribution of weights
cohortmeta %>%
    ggplot(aes(x = WEIGHT_MAX)) +
    geom_histogram(boundary = 0, binwidth = 10, color = 'black', fill = 'gray') +
    xlab("max weight during admission (KG)") +
    ylab("number of admissions") +
    ggtitle("Distribution of max weights by hospital admissions")

cohortmeta %>%
    ggplot(aes(x = WEIGHT_MAX, fill = GENDER)) +
    geom_histogram(boundary = 0, binwidth = 10, color = 'black', position = 'dodge') +
    xlab("max weight during admission (KG)") +
    ylab("number of admissions") +
    ggtitle("Distribution of max weights by hospital admissions (by gender)")

## check distribution of weights
cohortmeta %>%
    dplyr::group_by(SUBJECT_ID) %>%
    dplyr::summarize(WEIGHT_MAX = max(WEIGHT_MAX, na.rm = TRUE)) %>%
    dplyr::ungroup() %>%
    ggplot(aes(x = WEIGHT_MAX)) +
    geom_histogram(boundary = 0, binwidth = 10, color = 'black', fill = 'gray') +
    xlab("max weight during all admissions (KG)") +
    ylab("number of unique subjects") +
    ggtitle("Distribution of max weights by subjects")

## check distribution of ages
cohortmeta %>%
    ggplot(aes(x = AGE)) +
    geom_histogram(boundary = 0, binwidth = 1, color = 'black', fill = 'gray') +
    xlab("age at admission") +
    ylab("number of admissions") +
    ggtitle("Distribution of age by hospital admissions")

## check distribution of ages
cohortmeta %>%
    dplyr::mutate(AGE = pmin(AGE, 90)) %>%
    ggplot(aes(x = AGE)) +
    geom_histogram(boundary = 0, binwidth = 1, color = 'black', fill = 'gray') +
    scale_x_continuous("age at admission", breaks = seq(0, 1000, 5)) +
    ylab("number of admissions") +
    ggtitle("Distribution of age by hospital admissions")

## check distribution of genders
cohortmeta %>%
    ggplot(aes(x = GENDER)) +
    geom_bar(color = 'black', fill = 'gray') +
    ylab("number of admissions") +
    ggtitle("Distribution of genders by hospital admissions") +
    coord_flip()

## check distribution of genders
cohortmeta %>%
    dplyr::distinct(SUBJECT_ID, GENDER) %>%
    ggplot(aes(x = GENDER)) +
    geom_bar(color = 'black', fill = 'gray') +
    ylab("number of unique subjects") +
    ggtitle("Distribution of genders by subjects") +
    coord_flip()

## check distribution of length of stay
cohortmeta %>%
    ggplot(aes(x = LOS)) +
    geom_histogram(boundary = 0, binwidth = 5, color = 'black', fill = 'gray') +
    scale_x_continuous("length of admission (days)", breaks = seq(0, 1000, 100)) +
    ylab("number of admissions") +
    ggtitle("Distribution of length of stay by hospital admissions")
```

Check interaction of LOS and weight.

```{r, fig.width = 7, fig.height = 6}
## check LOS x weight
gp <- cohortmeta %>%
    dplyr::filter(HOSPITAL_EXPIRE_FLAG == 0L) %>%
    ggplot(aes(x = WEIGHT_MAX, y = LOS)) +
    geom_point(size = 1/2, alpha = 1/5) + 
    scale_x_continuous("max weight during admission", breaks = seq(0, 1000, 100)) +
    scale_y_continuous("length of admission (days)", breaks = seq(0, 1000, 100)) +
    ggtitle("Distribution of length of stay by hospital admissions",
            "only patients who didn't die during stay")
gp
gp + coord_cartesian(xlim = c(0, 300), y = c(0, 150))

cohortmeta %>%
    dplyr::filter(HOSPITAL_EXPIRE_FLAG == 0L) %>%
    dplyr::mutate(WEIGHT_MAX = cut_width(WEIGHT_MAX, boundary = 0, width = 10)) %>%
    ggplot(aes(x = WEIGHT_MAX, y = LOS)) +
    geom_boxplot(varwidth = TRUE) + 
    scale_x_discrete("max weight during admission", drop = FALSE) + 
    scale_y_continuous("length of admission (days)", breaks = seq(0, 1000, 100)) +
    ggtitle("Distribution of length of stay by hospital admissions",
            "only patients who didn't die during stay") +
    theme_x_rotate()

cohortmeta %>%
    dplyr::filter(HOSPITAL_EXPIRE_FLAG == 0L,
                  WEIGHT_MAX < 300) %>%
    dplyr::mutate(WEIGHT_MAX = cut_width(WEIGHT_MAX, boundary = 0, width = 10)) %>%
    ggplot(aes(x = WEIGHT_MAX, y = LOS)) +
    geom_quasirandom(varwidth = TRUE, size = 1/2, alpha = 1/2) + 
    geom_boxplot(varwidth = TRUE, alpha = 1/2, color = 'blue', outlier.shape = NA) + 
    scale_x_discrete("max weight during admission", drop = FALSE) + 
    scale_y_continuous("length of admission (days)", breaks = seq(0, 1000, 100)) +
    ggtitle("Distribution of length of stay by hospital admissions",
            "only patients who didn't die during stay") +
    theme_x_rotate()

cohortmeta %>%
    dplyr::filter(HOSPITAL_EXPIRE_FLAG == 0L,
                  WEIGHT_MAX < 300) %>%
    dplyr::mutate(WEIGHT_MAX = cut_width(WEIGHT_MAX, boundary = 0, width = 10)) %>%
    ggplot(aes(x = WEIGHT_MAX, y = LOS)) +
    geom_quasirandom(varwidth = TRUE, size = 1/2, alpha = 1/2) + 
    geom_boxplot(varwidth = TRUE, alpha = 2/3, color = 'blue', outlier.shape = NA) + 
    scale_x_discrete("max weight during admission", drop = FALSE) + 
    scale_y_continuous("length of admission (days)", breaks = seq(0, 1000, 10)) +
    ggtitle("Distribution of length of stay by hospital admissions",
            "only patients who didn't die during stay") +
    theme_x_rotate() +
    coord_cartesian(ylim = c(0, 50)) 

gp <- cohortmeta %>%
    dplyr::filter(HOSPITAL_EXPIRE_FLAG == 0L) %>%
    dplyr::mutate(WEIGHT_MAX = cut(WEIGHT_MAX, c(0, 80, 136, 1000))) %>%
    ggplot(aes(x = WEIGHT_MAX, y = LOS)) +
    geom_quasirandom(varwidth = TRUE, size = 1/2, alpha = 1/2) + 
    geom_boxplot(varwidth = TRUE, alpha = 2/3, color = 'blue', outlier.shape = NA) + 
    scale_x_discrete("max weight during admission", drop = FALSE) + 
    scale_y_continuous("length of admission (days)", breaks = seq(0, 1000, 10)) +
    ggtitle("Distribution of length of stay by hospital admissions",
            "only patients who didn't die during stay")
gp + coord_flip()
gp + coord_flip(ylim = c(0, 50))
```

Clear difference.

Simple OLS.

```{r}
summary(lm(LOS ~ WEIGHT_MAX,
           data = dplyr::filter(cohortmeta,
                                WEIGHT_MAX < 400,
                                HOSPITAL_EXPIRE_FLAG == 0L)))
```

Also check set of top events across all patients and notes (including children).

```{r}
turnevents %>%
    tidyr::unite(label, label, value, sep = "-") %>%
    dplyr::count(label, sort = TRUE)
```

Check for just our cohort.

```{r}
cohortturns %>%
    tidyr::unite(label, LABEL, VALUE, sep = "-") %>%
    dplyr::count(label, wt = n, sort = TRUE)
```

## Filtering and Adjustments

First, change age for older patients.

```{r}
cohortturns <- cohortturns %>%
    dplyr::mutate(AGE = pmin(AGE, 90))
```

Also remove anyone who has an unrealistic weight (>700).

```{r}
cohortmeta %>%
    dplyr::arrange(-WEIGHT_MAX) %>%
    dplyr::select(SUBJECT_ID, WEIGHT_MAX)
```

We will just remove those few cases where weight is over 600KG.

```{r}
cohortturns <- cohortturns %>%
    dplyr::filter(WEIGHT_MAX < 600)
```

# Analysis

## Total Counts

Examine high-level counts of recorded events across admissions.

```{r, fig.width = 8, fig.height = 3.5}
cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, GENDER, WEIGHT_MAX,
                 wt = n, name = "n") %>%
    dplyr::mutate(WEIGHT_BIN = cut(WEIGHT_MAX, c(0, 80, 136, 600))) %>%
    ggplot(aes(x = WEIGHT_BIN, y = n)) +
    geom_boxplot(varwidth = TRUE, outlier.alpha = 1/4) +
    xlab("max weight during admission (KG, binned)") +
    ylab("number of turn events") +
    ggtitle("Assocation between number of turn events and weight") +
    coord_flip()

cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, GENDER, WEIGHT_MAX, LOS,
                 wt = n, name = "n") %>%
    dplyr::mutate(WEIGHT_BIN = cut(WEIGHT_MAX, c(0, 80, 136, 600)),
                  scaled_n = n / LOS) %>%
    ggplot(aes(x = WEIGHT_BIN, y = scaled_n)) +
    geom_boxplot(varwidth = TRUE, outlier.alpha = 1/4) +
    xlab("max weight during admission (KG, binned)") +
    ylab("number of turn events per day") +
    ggtitle("Assocation between rate of turn events and weight") +
    coord_flip()
```

We can also bin by 20KG.

```{r, fig.width = 8, fig.height = 3.5}
cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, GENDER, WEIGHT_MAX,
                 wt = n, name = "n") %>%
    dplyr::mutate(WEIGHT_BIN = cut_width(WEIGHT_MAX,  boundary = 0, width = 20)) %>%
    ggplot(aes(x = WEIGHT_BIN, y = n)) +
    geom_boxplot(varwidth = TRUE, outlier.alpha = 1/4) +
    xlab("max weight during admission (KG, binned)") +
    ylab("number of turn events") +
    theme_x_rotate() +
    ggtitle("Assocation between number of turn events and weight")

cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, GENDER, WEIGHT_MAX, LOS,
                 wt = n, name = "n") %>%
    dplyr::mutate(WEIGHT_BIN = cut_width(WEIGHT_MAX,  boundary = 0, width = 20),
                  scaled_n = n / LOS) %>%
    ggplot(aes(x = WEIGHT_BIN, y = scaled_n)) +
    geom_boxplot(varwidth = TRUE, outlier.alpha = 1/4) +
    xlab("max weight during admission (KG, binned)") +
    ylab("number of turn events per day") +
    theme_x_rotate() +
    ggtitle("Assocation between rate of turn events and weight")
```

## By Type

Look at event types separately.

```{r, fig.width = 8, fig.height = 4}
gp <- cohortturns %>%
    dplyr::mutate(WEIGHT_BIN = cut(WEIGHT_MAX, c(0, 80, 136, 600)),
                  scaled_n = n / LOS) %>%
    ggplot(aes(x = WEIGHT_BIN, y = scaled_n)) +
    geom_boxplot(varwidth = TRUE, outlier.alpha = 1/4) +
    xlab("max weight during admission\n(KG, binned)") +
    ylab("number of turn events per day") +
    theme_x_rotate() +
    ggtitle("Assocation between rate of turn events and weight") +
    facet_grid(. ~ LABEL + VALUE)
gp + coord_flip()
gp + coord_flip(ylim = c(0, 2))
```

These distributions look a bit odd.

```{r}
cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, LOS, wt = n) %>%
    dplyr::mutate(nscaled = n / LOS) %>%
    dplyr::arrange(desc(nscaled))

cohortturns %>%
    dplyr::select(HADM_ID, SUBJECT_ID, AGE, LOS, VALUE, LABEL, n) %>%
    dplyr::mutate(nscaled = n / LOS) %>%
    dplyr::arrange(desc(nscaled))
```

We see that some of the admissions with high "rates" of turning are actually 
incredibly short stays (less than a single day). We can see how this looks.

```{r}
cohortturns %>%
    dplyr::distinct(HADM_ID, SUBJECT_ID, LOS) %>%
    dplyr::mutate(LOS = ceiling(LOS)) %>%
    ggplot(aes(x = LOS)) +
    geom_histogram(boundary = 1/2, binwidth = 1,
                   color = "black", fill = "gray") +
    xlab("length of stay (days)") +
    ylab("number of admissions")

cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, LOS, wt = n) %>%
    dplyr::mutate(nscaled = n / LOS) %>%
    dplyr::mutate(LOS = ceiling(LOS)) %>%
    dplyr::filter(LOS <= 50) %>%
    ggplot(aes(x = LOS, y = nscaled, group = LOS)) +
    geom_quasirandom(varwidth = TRUE, size = 1/2, alpha = 1/5) +
    geom_boxplot(color = '#E38191', fill = NA, outlier.shape = NA) +
    ylab("turn events per day")

cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, LOS, wt = n) %>%
    dplyr::mutate(nscaled = n / LOS) %>%
    dplyr::filter(LOS <= 50) %>%
    ggplot(aes(x = LOS, y = nscaled)) +
    geom_point(size = 1/2, alpha = 1/5) +
    stat_summary(aes(x = ceiling(LOS)), fun = median,
                 color = '#E38191', size = 1/2)
    ylab("turn events per day\n(median per days)")
```

Might make sense to exclude patients staying shorter than 48 hours.

```{r}
cohortturns <- cohortturns %>%
    dplyr::filter(LOS > 2)
```

Now look at this again by weight.

```{r, fig.width = 6, fig.height = 3.5}
cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, GENDER, WEIGHT_MAX, LOS,
                 wt = n, name = "n") %>%
    dplyr::mutate(scaled_n = n / LOS) %>%
    dplyr::mutate(WEIGHT_BIN = cut(WEIGHT_MAX, c(0, 80, 136, 600))) %>%
    ggplot(aes(x = WEIGHT_BIN, y = scaled_n)) +
    geom_quasirandom(alpha = 1/5, size = 1/2) + #, varwidth = TRUE) + 
    geom_boxplot(varwidth = TRUE, outlier.shape = NA,
                 color = '#E38191', fill = 'white', alpha = 1/4) +
    xlab("max weight during admission\n(KG, binned)") +
    ylab("turn events per day") +
    ggtitle("Assocation between number of turn events and weight") +
    coord_flip()
```

Split by type.

```{r, fig.width = 8, fig.height = 4}
gp <- cohortturns %>%
    dplyr::mutate(WEIGHT_BIN = cut(WEIGHT_MAX, c(0, 80, 136, 600)),
                  scaled_n = n / LOS) %>%
    ggplot(aes(x = WEIGHT_BIN, y = scaled_n)) +
    geom_boxplot(varwidth = TRUE, outlier.alpha = 1/4) +
    xlab("max weight during admission\n(KG, binned)") +
    ylab("number of turn events per day") +
    theme_x_rotate() +
    ggtitle("Assocation between rate of turn events and weight") +
    facet_grid(. ~ LABEL + VALUE)
gp + coord_flip()
gp + coord_flip(ylim = c(0, 2))
```

Also just look at counts (median evnts per day).

```{r}
cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, WEIGHT_MAX, LOS, wt = n) %>%
    dplyr::mutate(WEIGHT_BIN = cut(WEIGHT_MAX, c(0, 80, 136, 600)),
                  scaled_n = n / LOS) %>%
    dplyr::group_by(WEIGHT_BIN) %>%
    dplyr::summarize(Admissions = n(),
                     `Median Events` = median(scaled_n))

cohortturns %>%
    dplyr::count(HADM_ID, SUBJECT_ID, WEIGHT_MAX, LOS, wt = n) %>%
    dplyr::mutate(WEIGHT_BIN = cut_width(WEIGHT_MAX, boundary = 0, width = 20),
                  scaled_n = n / LOS) %>%
    dplyr::group_by(WEIGHT_BIN) %>%
    dplyr::summarize(Admissions = n(),
                     `Median Events` = median(scaled_n))
```
