---
title: "Analysis of Oral Care"
author: "Patrick Kimes"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
---

# Outline

Here we do simple word frequencies.

```{r}
library(tidyverse)
library(lubridate)
library(cowplot)
library(bigrquery)
library(ggbeeswarm)
library(stringr)
library(multcomp)

theme_set(theme_minimal())
theme_x_rotate <- function(...) {
    theme(axis.text.x = element_text(angle = 90, vjust = 1/2, hjust = 1), ...)
}

## bigrquery issue: https://github.com/r-dbi/bigrquery/issues/395
options(scipen = 20)
options(dplyr.summarise.inform = FALSE)
```

We will be querying from the same project and dataset on BigQuery.

```{r}
project <- "hst-953-2019"
bq_auth(email = "patrick.kimes@gmail.com")
```

Data tables will be saved to a local directory for easier future access.

```{r}
bqdir <- file.path("..", "data", "bigquery")
dir.create(bqdir, showWarnings = FALSE, recursive = TRUE)
```

# Data

## Ventilation

Read in ventilation records as parsed by Joy.

```{r}
vent_rds <- file.path(bqdir, "vent.rds")
if (file.exists(vent_rds)) {
    vent <- readRDS(vent_rds)
} else {
    bq_tab_vent <- "hst-953-2019.bias2020.ventilation_records"
    vent <- bq_table_download(bq_tab_vent, page_size = 1e3)
    saveRDS(vent, file = vent_rds)
}
```

Note that many of these ICU stays have no ventilation. These
records have NAs for total number and hours of ventilation.
We will replace these with 0s.

```{r}
vent <- vent %>%
    tidyr::replace_na(list(max_ventnum = 0,
                           total_hours = 0))
```

We also take the max number of ventilation events across
ICU stays for each hospital admission. We also take the 
total ventilation duration across the entire hospital 
admission.

```{r}
ventrecords <- vent %>%
    dplyr::group_by(subject_id, hadm_id) %>%
    dplyr::summarize(max_ventnum = max(max_ventnum),
                     total_hours = sum(total_hours)) %>%
    dplyr::ungroup()
```

## Oral Care

We also pull out oral care information.

```{r}
oralcare_rds <- file.path(bqdir, "oralcare.rds")
if (file.exists(oralcare_rds)) {
    oralcare <- readRDS(oralcare_rds)
} else {
    query <- paste("WITH",
                   "oralcare as (",
                   "  SELECT *",
                   "  FROM `hst-953-2019.bias2020.nursing_care_items` n",
                   "  WHERE n.type LIKE \"oral care\"",
                   "),",
                   "chart_records as (",
                   "  SELECT distinct",
                   "  subject_id, hadm_id, icustay_id, itemid, charttime",
                   "  FROM `physionet-data.mimiciii_clinical.chartevents`",
                   "  WHERE itemid IN (SELECT distinct itemid FROM oralcare)",
                   ")",
                   "SELECT c.*, o.label",
                   "FROM chart_records as c",
                   "LEFT JOIN oralcare as o",
                   "ON c.itemid = o.itemid",
                   "WHERE hadm_id IS NOT NULL",
                   "AND icustay_id IS NOT NULL",
                   sep = "\n")
    oc <- bq_project_query(x = "hst-953-2019", query = query)
    oralcare <- bq_table_download(oc)
    saveRDS(oralcare, oralcare_rds)
}
```

Count oral care events per hospital admission.

```{r}
ocrecords <- oralcare %>%
    dplyr::count(subject_id, hadm_id, name = "noralcare")
```

## Substance Use

We also pull in patients information with substance abuse information.

```{r}
subsabuse_rds <- file.path(bqdir, "subsabuse.rds")
if (file.exists(subsabuse_rds)) {
    subsabuse <- readRDS(subsabuse_rds)
} else {
    query <- paste("WITH", 
                   "ICD9_SUBSET AS (",
                   "  SELECT REPLACE (ICD9_CODE, \".\", \"\") AS ICD9_CODE, LONG_TITLE",
                   "  FROM `hst-953-2019.bias2020.icd9_substance_abuse`",
                   "),",
                   "ABUSE_DIAGNOSES AS (",
                   "  SELECT SUBJECT_ID, HADM_ID, ICD9_CODE, LONG_TITLE",
                   "  FROM `physionet-data.mimiciii_clinical.diagnoses_icd`",
                   "  INNER JOIN ICD9_SUBSET",
                   "  USING (ICD9_CODE)",
                   ")",
                   "SELECT *",
                   "FROM ABUSE_DIAGNOSES",
                   sep = "\n")
    sab <- bq_project_query(x = "hst-953-2019", query = query)
    subsabuse <- bq_table_download(sab)
    saveRDS(subsabuse, subsabuse_rds)
}
```

Change column names to lower case.

```{r}
subsabuse <- subsabuse %>%
    dplyr::rename_all(tolower)
```

Determine subject and admissions with either any substance abuse
or any alcohol abuse recorded. Read in a table to help us do this.

```{r}
icd9codes <- read_tsv(file.path("..", "data", "curated",
                                "icd-9-substanceabuse.tsv"),
                      col_types = cols(),
                      col_names = c("icd9_code", "long_title",
                                    "alcohol", "iv"),
                      skip = 1)
icd9codes <- icd9codes %>%
    dplyr::mutate(icd9_code = gsub("\\.", "", icd9_code)) 
```

```{r}
alcohol_ids <- subsabuse %>%
    dplyr::inner_join(icd9codes %>%
                      dplyr::filter(alcohol == "YES") %>%
                      dplyr::select(icd9_code),
                      by = "icd9_code") %>%
    dplyr::distinct(subject_id, hadm_id)

iv_ids <- subsabuse %>%
    dplyr::inner_join(icd9codes %>%
                      dplyr::filter(iv == "YES") %>%
                      dplyr::select(icd9_code),
                      by = "icd9_code") %>%
    dplyr::distinct(subject_id, hadm_id)

anysubs_ids <- subsabuse %>%
    dplyr::distinct(subject_id, hadm_id)
```

Check how many total admissions.

```{r}
nrow(anysubs_ids)
nrow(alcohol_ids)
nrow(iv_ids)
```

## Cohort

Determine and extract the same cohort as Joy.

This query performs the following operations to return a 
cohort table.

1. Take unique hospital admissions, add a few metadata fields
and filter on admissions with chartevent data.
2. Determine the total ICU length of stay using the `los` field 
in the ICU stays table.
3. Determine the average age, oasis score, oasis prob, and mechanical
ventilation indicator for each hospital admission using the OASIS
derived table.
4. Add Elixhauser score along with OASIS score and ICU length of stay
to cohort table.

```{r}
joycohort_rds <- file.path(bqdir, "joycohort.rds")
if (file.exists(joycohort_rds)) {
    joycohort <- readRDS(joycohort_rds)
} else {
    query <- paste("WITH",
                   "patients as (",
                   "  SELECT distinct",
                   "    w.subject_id, w.hadm_id, gender, a.ethnicity, ",
                   "    dob, weight_max, height_max",
                   "  FROM `hst-953-2019.bias2020.notes_by_weight` w",
                   "  LEFT JOIN `physionet-data.mimiciii_clinical.admissions` a",
                   "  USING (subject_id, hadm_id)",
                   "  WHERE a.has_chartevents_data = 1",
                   "),",
                   "icustay as (",
                   "  SELECT distinct ",
                   "    subject_id, hadm_id, sum(los) as icu_los",
                   "  FROM `physionet-data.mimiciii_clinical.icustays`",
                   "  GROUP BY subject_id, hadm_id",
                   "),",
                   "oasis AS (",
                   "  SELECT distinct",
                   "    hadm_id, avg(age) as age, ",
                   "    avg(oasis) as ave_oasis_prob, ",
                   "    avg(oasis) as ave_oasis, ",
                   "    max(mechvent) as mechvent",
                   "  FROM `physionet-data.mimiciii_derived.oasis`",
                   "  GROUP BY hadm_id",
                   "),",
                   "cohort AS (",
                   "  SELECT distinct ",
                   "    pt.*, o.age, i.icu_los, e.elixhauser_sid30,",
                   "    o.ave_oasis_prob, o.ave_oasis, o.mechvent",
                   "  FROM patients as pt",
                   "  LEFT JOIN icustay as i",
                   "  ON pt.subject_id = i.subject_id",
                   "  AND pt.hadm_id = i.hadm_id",
                   "  LEFT JOIN `physionet-data.mimiciii_derived.elixhauser_quan_score` e",
                   "  ON pt.hadm_id = e.hadm_id ",
                   "  LEFT JOIN  oasis o",
                   "  ON pt.hadm_id = o.hadm_id",
                   ")",
                   "SELECT distinct * FROM cohort",
                   sep = "\n")
    jco <- bq_project_query(x = "hst-953-2019", query = query)
    joycohort <- bq_table_download(jco)
    saveRDS(joycohort, joycohort_rds)
}
```

Clean up the age and split weight into cohort groups.

```{r}
joycohort <- joycohort %>%
    dplyr::mutate(age = if_else(age > 100, 95, age),
                  cohort = cut(weight_max, c(0, 80, 136, Inf)))
```

Combine data tables.

```{r}
fulldat <- joycohort %>%
    dplyr::left_join(ventrecords, by = c("subject_id", "hadm_id")) %>%
    dplyr::left_join(ocrecords, by =  c("subject_id", "hadm_id"))
```

Add substance abuse labels to the cohort table.

```{r}
fulldat <- fulldat %>%
    dplyr::left_join(dplyr::mutate(anysubs_ids, substance = "reported"),
                     by = c("subject_id", "hadm_id")) %>%
    dplyr::left_join(dplyr::mutate(alcohol_ids, alcohol = "reported"),
                     by = c("subject_id", "hadm_id")) %>%
    dplyr::left_join(dplyr::mutate(iv_ids, iv = "reported"),
                     by = c("subject_id", "hadm_id")) %>%
    tidyr::replace_na(list(substance = "none",
                           alcohol = "none",
                           iv = "none")) %>%
    dplyr::mutate(substance = factor(substance),
                  alcohol = factor(alcohol),
                  iv = factor(iv))
```

Convert some columns into factors.

```{r}
fulldat <- fulldat %>%
    dplyr::mutate(ethnicity = case_when(
                      grepl("WHITE", ethnicity) ~ "WHITE",
                      grepl("BLACK", ethnicity) ~ "BLACK",
                      grepl("(ASIAN|MIDDLE EASTERN)", ethnicity) ~ "ASIAN",
                      grepl("(HISPANIC|LATINO|CARIBEAN|SOUTH AMERICAN)",
                            ethnicity) ~ "HISPANIC",
                      TRUE ~ "OTHER")) %>%
    dplyr::mutate_at(c("gender", "ethnicity"), factor)

fulldat <- fulldat %>%
    dplyr::mutate(ethnicity = fct_relevel(ethnicity, c("WHITE", "BLACK", "ASIAN",
                                                       "HISPANIC", "OTHER")))
```

Count number of occurrences of NAs in data.

```{r}
fulldat %>%
    dplyr::summarize_all(~sum(is.na(.))) %>%
    t()
```

We have NAs in many columns, including DOB, Elixhauser score and number of
oral care events. We'll assume the NAs for oral care are zeros - this needs to be
clarified with Joy. This is a reasonable assumption considering these patients
are filtered to be only those with chart events recorded.

```{r}
fulldat <- fulldat %>%
    tidyr::replace_na(list(noralcare = 0L))
```

# Filtering

Count up the number of admissions where patient was on mechanical
ventilator.

```{r}
fulldat %>%
    dplyr::count(mechvent, cohort) %>%
    tidyr::pivot_wider(names_from = cohort, values_from = n)

fulldat %>%
    dplyr::count(mechvent, cohort) %>%
    dplyr::group_by(cohort) %>%
    dplyr::mutate(n = round(n / sum(n), 3)) %>%
    tidyr::pivot_wider(names_from = cohort, values_from = n)
```

Count up number of minors.

```{r}
fulldat %>%
    dplyr::count(age = cut(age, c(0, 18, Inf),
                           include.lowest = TRUE))
```

We will filter patient cohort based on several clinical features.

```{r}
fulldat <- fulldat %>%
    dplyr::filter(!is.na(age), age > 18,
                  weight_max < 600,
                  mechvent == 1L)
```

# Analysis: Weight

See that heavier patients are more likely to have been on 
mech vent at some point during the admission. We will only 
use stays that involve the patient being placed on mech vent.

```{r, fig.width = 5, fig.height = 4}
gpbox <- fulldat %>%
    ggplot(aes(x = cohort, y = noralcare)) +
    geom_quasirandom(alpha = 1/2, pch = 21, fill = 'gray') +
    geom_boxplot(alpha = 0, varwidth = TRUE, outlier.shape = NA) + 
    ggtitle("Number of oral care events by weight")
    
gpbox +
    ylab("number of oral care events") +
    xlab("Weight Group")

gpbox +
    scale_y_continuous("number of oral care events", trans = "log10") +
    xlab("Weight Group")
```

Look at this differently - namely, filter out patients with stays 
less than 24 hours and calcualte the rate.

```{r, fig.width = 6, fig.height = 3.5}
fulldat %>%
    dplyr::filter(total_hours > 24) %>%
    ggplot(aes(x = cohort, y = noralcare / total_hours * 24)) +
    geom_quasirandom(alpha = 1/2, pch = 21, fill = 'gray') +
    geom_boxplot(alpha = 1/2, fill = 'white', color = 'red',
                 varwidth = TRUE, outlier.shape = NA) + 
    ggtitle("Average daily number of oral care events by weight",
            "patients w/ >24 hours on ventilator") +
    coord_flip() + 
    ylab("number of oral care events") +
    xlab("Weight Group")
```

## Models

We now fit a simple Poisson model with length of time on mechanical 
ventilator as an offset.

```{r}
pfit <- glm(formula = noralcare ~ 1 + cohort,
            offset = log(total_hours), family = "poisson",
            data = fulldat)
summary(pfit)
```

Perform the full pairwise comparison of all `cohort` levels.

```{r}
summary(glht(pfit, mcp(cohort = "Tukey")))
```

Also correct for various other variables.

```{r}
pfit <- glm(formula = noralcare ~ 1 + gender + ethnicity + age +
                ave_oasis + elixhauser_sid30 + cohort,
            offset = log(total_hours), family = "poisson",
            data = fulldat)
summary(pfit)
```

Perform the full pairwise comparison of all `cohort` levels.

```{r}
summary(glht(pfit, mcp(cohort = "Tukey")))
```

Effect is similar even after correcting for other patient demographics.

# Analysis: Alcohol

Count number of patients with alcohol use reported during admission.

```{r}
fulldat %>%
    dplyr::count(alcohol)
```

Check to see how patients with alcohol abuse might differ from
other patients.

```{r, fig.width = 5, fig.height = 4}
gpbox <- fulldat %>%
    ggplot(aes(x = alcohol, y = noralcare)) +
    geom_quasirandom(alpha = 1/2, pch = 21, fill = 'gray', varwidth = TRUE) +
    geom_boxplot(alpha = 0, varwidth = TRUE, outlier.shape = NA) + 
    ggtitle("Number of oral care events by weight")
    
gpbox +
    ylab("number of oral care events") +
    xlab("Weight Group")

gpbox +
    scale_y_continuous("number of oral care events", trans = "log10") +
    xlab("Weight Group")
```

Look at this differently - namely, filter out patients with stays 
less than 24 hours and calcualte the rate.

```{r, fig.width = 6, fig.height = 3.5}
fulldat %>%
    dplyr::filter(total_hours > 24,
    (alcohol == "reported") |
    (substance == "none")) %>%
    ggplot(aes(x = alcohol, y = noralcare / total_hours * 24)) +
    geom_quasirandom(alpha = 1/2, pch = 21, fill = 'gray') +
    geom_boxplot(alpha = 1/2, fill = 'white', color = 'red',
                 varwidth = TRUE, outlier.shape = NA) + 
    ggtitle("Average daily number of oral care events",
            "patients w/ >24 hours on ventilator") +
    coord_flip() + 
    ylab("number of oral care events") +
    xlab("Alcohol Abuse")
```

Actually see higher rates of oral events.

## Models

We now fit a simple Poisson model with length of time on mechanical 
ventilator as an offset.

```{r}
pfit <- glm(formula = noralcare ~ 1 + alcohol,
            offset = log(total_hours), family = "poisson",
            data = fulldat %>%
                dplyr::filter((alcohol == "reported") |
                              (substance == "none")))
summary(pfit)
```

```{r}
pfit <- glm(formula = noralcare ~ 1 + gender + ethnicity +
                age + ave_oasis + elixhauser_sid30 + alcohol,
            offset = log(total_hours), family = "poisson",
            data = fulldat %>%
                dplyr::filter((alcohol == "reported") |
                              (substance == "none")))
summary(pfit)
```

In both models, we see a slightly higher rate of oral events in 
this population.

```{r}
exp(.11)
```

About 11% higher than in non-alcohol patients.

# Analysis: IV Drug

Count number of patients with IV drug use reported during admission.

```{r}
fulldat %>%
    dplyr::count(iv)
```

## Models

We now fit a simple Poisson model with length of time on mechanical 
ventilator as an offset.

```{r}
pfit <- glm(formula = noralcare ~ 1 + iv,
            offset = log(total_hours), family = "poisson",
            data = fulldat %>%
                dplyr::filter((iv == "reported") |
                              (substance == "none")))
summary(pfit)
```

```{r}
pfit <- glm(formula = noralcare ~ 1 + gender + ethnicity +
                age + ave_oasis + elixhauser_sid30 + iv,
            offset = log(total_hours), family = "poisson",
            data = fulldat %>%
                dplyr::filter((iv == "reported") |
                              (substance == "none")))
summary(pfit)
```

Again, we see a slightly higher rate of oral events in 
this population.


 
